Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-16 report/report.tex
Update todo
Add main conclusion to the scientific study

% Thursday:
% TODO: Write introduction section
    % TODO: Figure showing the unique characteristics of footpaths vs other road types (OSM Screeshot)
    % TODO: Virtual city picture
    % TODO: read Vanega
% TODO: Write Collision study implementation section
    % TODO: Figure detailing the steps in the point-matching algorithm
    % TODO: Edge distance algorithm, outline, algorithm + picture

% Scietific study
% TODO: Find papers and topics for the scientific study (Building footprints, building heights, LOD levels, road rendering, terrain (Procedural roads))
% TODO: Scientific study, disposition
    % TODO: Scientific study: Potential application: A method of generating cities on the cheap
% TODO: Scientific study: A set of recommendations.

@@

>>>>

% Writing:
% TODO: Write introduction section
    % TODO: read Vanega
% TODO: Write Collision study implementation section
    % TODO: Edge distance algorithm, algorithm

% Pictures
% Introduction
    % TODO: Figure showing the unique characteristics of footpaths vs other road types (OSM Screeshot)
    % TODO: Virtual city picture
% Collision study implementation
    % TODO: Figure detailing the steps in the point-matching algorithm
    % TODO: Edge distance algorithm, picture

% Scietific study
    % TODO: Find papers and topics for the scientific study (Building footprints, building heights, LOD levels, road rendering, terrain (Procedural roads))
    % TODO: Scientific study, disposition

@@

The main conclusion is that generating virtual cities purely from OpenStreetMap data is a perfectly feasibile procedure in the media industry, with the inclusion of procedural methods such as shape grammars to generate detail.
It will be a cheap method that reuires minimum effort in terms of source data collection. And the shape grammar method allows for a great deal of scalability.
The level of detail of individual models and the composition as a whole can be fitted to the scope of the project and the team size.
In the area of urban design however, urban planners often require complementary data to build morphological representations of the data that they are working with.
The feasibility of creating virtual cities that are of use to urban planners will depend mainly on the availablity of that complementary data.
